Appendix

### 2019-07-19 figures/07_model-selection.Rmd
figure combine + cleanup

```{r tp_summary, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[1]] # 1 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

gg_tp_fe <- ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) +
  xlab("")

gg_tp_fe
```

@@

```{r tn_summary, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

gg_tn_fe <- ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) +
  xlab("")

gg_tn_fe
```

@@

>>>>

```{r tp_fe, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[1]] # 1 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

gg_tp_fe <- ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) +
  xlab("") 
```

@@

```{r tn_fe, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

gg_tn_fe <- ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  theme_cowplot() +
  ylim(-0.6, 0.4) +
  ylab("Standardized FE slope") + theme(legend.position = 0) +
  xlab("") 
```

@@

```{r fe}
cowplot::plot_grid(gg_tp_fe + theme(axis.title.x = element_blank()), 
                   gg_tn_fe + theme(axis.text.y = element_blank(), 
                                    axis.title.x = element_blank()), 
                   rel_widths = c(1, 0.6))
```

```{r re}
cowplot::plot_grid(gg_tp_re, 
                   gg_tn_re + theme(axis.text.y = element_blank(), 
                                    axis.title.y = element_blank()), 
                   rel_widths = c(1, 0.9))
```

### 2019-07-19 manuscript/appendix.Rmd
figure combine + cleanup

dt_waffle <- tidyr::gather(dt, key = "key", value = "value", -`Trophic State`) %>%
  add_row(`Trophic State` = "oligotrophic", `key` = "All Lakes", `value` = 2) %>%
  add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
  arrange(`Trophic State`)

ggplot(dt_waffle,
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=0.7, n_rows = 5) +
  facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 2))

>>>>

dt_waffle <- tidyr::gather(dt, key = "key", value = "value", -`Trophic State`) %>%
  add_row(`Trophic State` = "oligotrophic", `key` = "All Lakes", `value` = 2) %>%
  add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
  arrange(`Trophic State`) %>%
  dplyr::filter(key == "This Study")

ggplot(dt_waffle,
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = TRUE) +
  # facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 2))
